Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-04 paper/main.tex
add bootstrap error lines to fig 3 and a little discussion
addressing final comments from PR

% codes
\newcommand{\pzcode}[1]{\texttt{#1}}
\newcommand{\qp}{\pzcode{qp}}
\newcommand{\annz}{\pzcode{ANNz2}}
\newcommand{\bpz}{\pzcode{BPz}}
\newcommand{\cmnn}{\pzcode{CMNN}}
\newcommand{\delight}{\pzcode{Delight}}
\newcommand{\eazy}{\pzcode{EAZY}}
\newcommand{\flexzboost}{\pzcode{FlexZBoost}}
\newcommand{\gpz}{\pzcode{GPz}}
\newcommand{\lephare}{\pzcode{LePhare}}
\newcommand{\metaphor}{\pzcode{METAPhoR}}
\newcommand{\skynet}{\pzcode{SkyNet}}
\newcommand{\tpz}{\pzcode{TPZ}}
\newcommand{\trainz}{\pzcode{trainZ}}

@@

\begin{document}
\linenumbers

@@

Many scientific investigations of photometric galaxy surveys require redshift estimates, whose uncertainty properties are best encapsulated by photometric redshift (photo-$z$) posterior probability distribution functions (PDFs).
A plethora of photo-$z$ PDF estimation methodologies abound, producing discrepant results with no consensus on a preferred approach.
We present the results of a comprehensive experiment comparing twelve photo-$z$ algorithms on mock data produced for the Large Synoptic Survey Telescope (\textsc{LSST}) Dark Energy Science Collaboration (\textsc{DESC}).
By supplying perfect prior information, in the form of the complete template library and a representative training set as inputs to each code, we demonstrate the impact of the assumptions underlying each technique on the output photo-$z$ PDFs.
In the absence of a notion of true, unbiased photo-$z$ PDFs, we evaluate and interpret multiple metrics of the ensemble properties of the derived photo-$z$ PDFs as well as traditional reductions to photo-$z$ point estimates.
We report systematic biases and overall over/under-breadth of the photo-$z$ PDFs of many popular codes, which may indicate avenues for improvement in the algorithms or implementations.
Furthermore, we raise attention to the limitations of established metrics for assessing photo-$z$ PDF accuracy; though we identify the conditional density estimate (CDE) loss as a promising metric of photo-$z$ PDF performance in the case where true redshifts are available but true photo-$z$ PDFs are not, we emphasize the need for science-specific performance metrics.

@@

{ \red{personal funding sources}}
S.~Schmidt acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM is advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.

>>>>

% codes
\newcommand{\pzcode}[1]{\texttt{#1}}
\newcommand{\qp}{\pzcode{qp}}
\newcommand{\annz}{\pzcode{ANNz2}}
\newcommand{\bpz}{\pzcode{BPZ}}
\newcommand{\cmnn}{\pzcode{CMNN}}
\newcommand{\delight}{\pzcode{Delight}}
\newcommand{\eazy}{\pzcode{EAZY}}
\newcommand{\flexzboost}{\pzcode{FlexZBoost}}
\newcommand{\gpz}{\pzcode{GPz}}
\newcommand{\lephare}{\pzcode{LePhare}}
\newcommand{\metaphor}{\pzcode{METAPhoR}}
\newcommand{\skynet}{\pzcode{SkyNet}}
\newcommand{\tpz}{\pzcode{TPZ}}
\newcommand{\trainz}{\pzcode{trainZ}}

@@

% ======================================================================
%\hypersetup{draft}
\begin{document}
\linenumbers

@@

Many scientific investigations of photometric galaxy surveys require redshift estimates, whose uncertainty properties are best encapsulated by photometric redshift (photo-$z$) posterior probability distribution functions (PDFs).
A plethora of photo-$z$ PDF estimation methodologies abound, producing discrepant results with no consensus on a preferred approach.
We present the results of a comprehensive experiment comparing twelve photo-$z$ algorithms applied to mock data produced for the Large Synoptic Survey Telescope (\textsc{LSST}) Dark Energy Science Collaboration (\textsc{DESC}).
By supplying perfect prior information, in the form of the complete template library and a representative training set as inputs to each code, we demonstrate the impact of the assumptions underlying each technique on the output photo-$z$ PDFs.
In the absence of a notion of true, unbiased photo-$z$ PDFs, we evaluate and interpret multiple metrics of the ensemble properties of the derived photo-$z$ PDFs as well as traditional reductions to photo-$z$ point estimates.
We report systematic biases and overall over/under-breadth of the photo-$z$ PDFs of many popular codes, which may indicate avenues for improvement in the algorithms or implementations.
Furthermore, we raise attention to the limitations of established metrics for assessing photo-$z$ PDF accuracy; though we identify the conditional density estimate (CDE) loss as a promising metric of photo-$z$ PDF performance in the case where true redshifts are available but true photo-$z$ PDFs are not, we emphasize the need for science-specific performance metrics.

@@

{ \red{personal funding sources}}
S.~Schmidt acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
